Resource Use and the Value-Productivity Tradeoff in Australian Winegrowing Regions

### 2023-06-22 article.tex
updated r analysis file, fixing continuity in variable use and fixing graph construction. updated reference list to include three articles on value vs quantity tradeoff in agri sector. added a requirements file for python libraries. updated the article with further edits and tables - a lot still to do.

\section{Introduction}
When assessing strategies for viticulture there is a trade-off between the amount of resources invested and the resultant quality and quantity of grapes produced \autocite{montalvo-falconSustainabilityResearchWine2023}. Due to recent economic, social and environmental pressures, such as: bush fires, tariffs, and shifting attitudes to alcohol consumption; the chosen emphasis taken in balancing the value-productivity tradeoff has become more important \autocite{toumbourouStudentSurveyTrends2018,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2022}. When considering pressures such as those prior listed, the integration of viticulture within the Australian wine industry is a compounding effect.

In this analysis we observed relationships between quantity and quality through the use of linear models. For the purpose of this study; quality was defined by the financial value of grapes per tonne. An extensive amount of research into a variety of factor's effect on grape quality and yield exists. Due to the lack of long-term and in-depth data sources, individual effects are often studied in isolation \autocite{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insight at a large scale across multiple regions \autocite{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions.

@@

Limitations included overestimating yield for models 1 and 2, (see Figures 1 and 2) and underestimating crop value in models 3 and 4 (see Figures 3 and 4).

 Reviewing the data to uncover reasons for this included the use of binary variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost; however none of these variables were able to explain why some vineyards produced less, or why other vineyards sold at higher prices than predicted. A wide variety of these influences were likely already explained within the use of year and GI Region, or the interaction of both variables. The change between some regions was dramatic, with particularly warmer and drier regions producing much higher volumes of grapes at lower prices (See Figures 5 and 6). The use of other variables and methods, specifically splines, were able to create a more normally distributed set of residuals but at a drastically reduced accuracy when comparing R2 and RSE. The introduction of known average prices per tonne also helped increase R2 values a small amount; it is important to not that it is common practice for wineries to purchase grapes at a regional average rate, likely resulting in much less variance within a region.

@@

>>>>

\section{Introduction}

The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. When strategies for a sustainable industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant quality verses quantity of crops produced. This dilemma exists across agriculture, sharing fundemental considerations such as water and nitrogen input \autocite{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016,zhuEffectsNitrogenLevel2017}. Within viticulture (the cultivation of grapes for wine production) quality is driven by its integration within the wine industry; with a wine's potential quality being initially defined through the chemical makeup of the grapes used in its production. The consideration of sustainability is further complicated by environmental and socio-demographic pressures. In the Australian context, these include biosecurity, climate and international market demands.

In this analysis we observe relationships between quantity and quality through the use of linear models. Quality can be defined in a variety of ways for grapes, such as # # #. For the purpose of this study quality was defined by the financial value of grapes per tonne; this was due to varying differences in defining quality between grape varietals.

An extensive amount of research into a variety of factor's effect on grape quality and yield exists. Due to the lack of long-term and in-depth data sources, individual effects are often studied in isolation \autocite{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insight at a large scale across multiple regions \autocite{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions.

@@

Limitations included overestimating yield for models 1 and 2, (see Figures 1 and 2) and underestimating crop value in models 3 and 4 (see Figures 3 and 4).
% This section needs to be heavily revised. Why are there tails on the distributions? What does a heavy tail indicate?
% What does it look like with respect to disaster events?
% split the discussion sections out of the results!! Even the questions I am asking are answered in the discussion, however they need to be highlighted as aspects of the models here beforehand.
 Reviewing the data to uncover reasons for this included the use of binary variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost; however none of these variables were able to explain why some vineyards produced less, or why other vineyards sold at higher prices than predicted. A wide variety of these influences were likely already explained within the use of year and GI Region, or the interaction of both variables. The change between some regions was dramatic, with particularly warmer and drier regions producing much higher volumes of grapes at lower prices (See Figures 5 and 6). The use of other variables and methods, specifically splines, were able to create a more normally distributed set of residuals but at a drastically reduced accuracy when comparing R2 and RSE. The introduction of known average prices per tonne also helped increase R2 values a small amount; it is important to not that it is common practice for wineries to purchase grapes at a regional average rate, likely resulting in much less variance within a region.

@@

% It is odd to have a paragraph on its own without a label, it does look a bit lost in the article.
The correlation between average sales price and yield was a negative trend (see table 2); the contributing factors to yield and average sales price was ???. Correlation values showed that water and emissions increased with yield but decreased with average sale price (see Table 4). In alternative attempts at models it was found that without the incorporation of GI Region or year the predictions greatly under performed. The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. % ALSO THAT CATASTROPHES HAPPEN EVEN ON SMALL SCALES THis needs to be tied up better.
 This is most notable when grouping regions by climate, especially when considering GI Regions in the 'Hot Very Dry' climate (see Figure 7). The effect of climate in the models was not more significant than the more granular use of GI regions. The interaction between year and GI Region likely accounted for localised events such as bushfires, which would be impactful, but only at a local level in both time and space.

%\begin{figure}
%  \includegraphics[width=\linewidth]{figure7.jpg}
%  \caption{A depiction of the relationship between Value of tonnes harvested per hectare and yield per hectare.Both variables have been transformed to be scaled by standard deviation with mean 0.}
%  \label{fig:fig7}
%\end{figure}

\subsection{Model Validation}
To validate the performance of these models k-fold cross validation was used. This was done using 10 folds, k=10, repeated 100 times. The models performed similarly to their original counter parts (see Table 11).

% really this is it?

\begin{table}[]
  \label{tab:tab12}
  \caption{Model validation using k-fold cross validation, for 10 folds repeated 100 times.}
  \begin{tabular}{llll}
          & RMSE      & R2        & MAE       \\
  Model 1 & 3.087E-01 & 9.045E-01 & 2.165E-01 \\
  Model 2 & 5.104E-01 & 7.409E-01 & 3.493E-01 \\
  Model 3 & 1.652E-01 & 9.723E-01 & 1.008E-01 \\
  Model 4 & 2.235E-01 & 9.500E-01 & 1.279E-01
  \end{tabular}
  \end{table}

\section{Discussion}
% this needs serious revision.
This study investigated the general relationships between input resources of a vineyard, including fuel and water, and the outputs including yield and value. Some regions appeared to produce many low quality grapes at scale compared to attempting to produce fewer higher quality grapes. This behaviour can be observed when reviewing Wine Australia’s annual reports, where it is apparent that warm inland regions such as the Riverland are known to only produce large amounts of lower graded grapes \autocite{wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2017}. Comparatively, regions such as Tasmania only produce A grade grapes but in much smaller quantities than the Riverland. Knowing that the difference in pricing per tonne can exceed a magnitude of 10 between grades E and A, the operations in regions that target different grades would have varied priorities. However, some regions such as the Yarra Valley produce a Variety of different grades of grapes, from C to A, highlighting that vineyard priorities, although may be somewhat present within regional classifications, are not necessarily aligned within a given region.

The opportunity to target different grades of grapes may not always be available, with some regions being more renowned than others, and likely to be sought after regardless \autocite{hallidayAustralianWineEncyclopedia2009}. The Barossa is an example of this, known for its quality could also lend itself to a bias in purchasers not considering other regions that may be capable of similar quality. This effect could stifle the potential for market opportunities within these lesser known regions. A further possibility is that there may be regional upper limits with the relationship between resource input and the value gained becoming no longer proportional due to diminishing returns. Climate was considered to be a large determinant of the ability to grow a larger quantity of grapes, as well as a determinant in grape quality \autocite{agostaRegionalClimateVariability2012}; however there were vineyards in similar regions that were able to produce exceptionally better results than others (See Figure 7).

The issue of model 1 and 2 over predicting yield, may have been due to preventative measures brought on by regional pressures such as fire, frost and disease. Where, more resources were required to prevent these issues from spreading within a region, thus disproportionately effecting some vineyards compared to others locally. This type of maintenance is not well captured especially when considering that some regions, those in warmer areas are not as prone to disease as cooler climates and could potentially have lower operating costs per hectare. This could create a discrepancy in vineyards that utilise preventative measures in wetter regions, as opposed to those who do not, and thus expend less fuel and energy but risk disease. When reviewing the differences between regions it is important to consider that vineyards in Hot Very Dry areas can be hundreds of times the size of those in other regions. It is interesting that while area, although significantly correlated to the ratio of yield to area, was still lower than water and about the same as emissions. This points to economies of scale playing a role but still being only one consideration alongside the potential resources that can be used. The negative trend between size and average sales price could also be a side effect of mass supply verse demand, especially when looking at the level of difference in production of some vineyards (see Table 4). The relationships between yield, value and area are not simply about efficiently producing the most grapes; sales price and by association grape quality, are integral to the profitability, and this is strongly linked to resource use and thus the longevity and sustainability of a vineyard.

Literature shows that there are many on-the-ground decisions that influence both quality and yield. Where these decisions are governed by complex physical and social forces such as international market demands, disease pressures and natural disasters \autocite{abadCoverCropsViticulture2021,cortezUsingDataMining2009,hallWithinseasonTemporalVariation2011,i.goodwinManagingSoilWater2009,kasimatiPredictingGrapeSugar2022,oliverReviewSoilPhysical2013,srivastavaNondestructiveSensingMethods2018}. Many of these occurrences being highlighted throughout the past decades vintage reports \autocite{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}. %This definitely needs to be broken up, what were these occurences, which year was significant for what?
It is also important to consider that these reports show that the warm inland regions have seen a decline in profit during this period, as they were often compared to other regions that focused more on quality than quantity. This is an important consideration, as the size of some of these vineyards when considering their ratio of value to area would only require a marginal increase to out compete other regions. There are also differences when comparing winegrowers to other agricultural industries as they are vertically integrated within the wine industry, tying them to secondary and tertiary industries, such as wine production, packaging, transport and sales. This results in unique issues and considerations for each vineyard, where these on-the-ground decisions may be influenced by other wine industry's choices, such as the use of sustainable practices in vineyards as a requirement for sale in overseas markets; notably these interactions are further complicated by some winegrowers being totally integrated into wine companies, while others are not (Knight et al., 2019). Incorporating such decisions into the model could help describe the contributing factors to regional differences beyond resource consumption and regional differences.

Having more data for each region would also be an improvement, allowing greater comparison between regions. More variables may also help to discern vineyards that can produce larger volumes of grapes at higher prices. The use of semi transparent tools such as random forests and decision trees alongside more variables and data may help to uncover the reasons for values that were under or over estimated. These differences could be caused by the use of alternative sustainable practices in the field. While there is evidence to suggest that environmentally sustainable practices can reduce costs, increase efficiency, whilst improving the quality of grapes, more research is needed to link these benefits across different regions and climates \autocite{baianoOverviewSustainabilityWine2021,marianiSustainableWinegrowingCurrent2015,montalvo-falconSustainabilityResearchWine2023}.
